Fusion Moves for Correlation Clustering

### 2014-11-05 paper/egpaper_for_review.tex
fubar

\subsection{Real World Models}
An example for large scale correlation clustering is 
segmentation of region adjacency graphs (RAG) for
3D closed surface segmentation of neural tissue data 
\cite{kroeger_2012_eccv}.
The energy is based on a likelihood of merging adjacent super-voxels.
Each edge has a probability to keep adjacent segments separate ($p(y_{ij} =1)$)
or to merge them ($p(y_{ij} = 0)$).
The energy function is defined as following.
\begin{align}
 J(y)  &= \sum_{ij \in E} y_{ij}\cdot \underbrace{  log\left( \frac{p(y_{ij} =0)}{p(y_{ij} =1)}\right) + log \frac{1-\beta}{\beta}  }_{w_{ij}}
\end{align}
Where $\beta$ is used as a prior.
Models of different size are included in the graphical model
benchmark of Kappes \etal ~\cite{kappes_2013_benchmark_cvpr} (???).
We use models with the cube sizes $300^3$, $450^3$, $550^3$ and $900^3$.
The number of variables varies from ??? to ???, and the number
of edges from ??? to ???.

\begin{center}
    \begin{figure}
        \begin{center}
            \begin{subfigure}[b]{0.45\linewidth}
                \includegraphics[width=1.0\linewidth]{images/-010.jpg}
            \end{subfigure}
            \quad
            \begin{subfigure}[b]{0.45\linewidth}
                \includegraphics[width=1.0\linewidth]{images/-030.jpg}
            \end{subfigure}
        \end{center}
    \caption{
        Raw FIBSEM data and correlation clustering result of the model from \cite{kroeger_2012_eccv}
    }
    \end{figure}
\end{center}

@@

\newpage
{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\newpage
\onecolumn
\section{Appendix}

>>>>

\subsection{Real World Models}
To segment images or volumes into a previously
unknown number of clusters, correlation clustering
can be used.
Starting from a super-pixel / super-voxel segmentation
which defines a region adjacency graphs (RAG),
correlation clustering finds the cut with the lowest energy.
The energy is based on a likelihood of merging adjacent super-voxels.
Each edge has a probability to keep adjacent segments separate ($p(y_{ij} =1)$)
or to merge them ($p(y_{ij} = 0)$).
The energy function is defined as following:
\begin{align}
 J(y)  &= \sum_{ij \in E} y_{ij}\cdot \underbrace{  log\left( \frac{p(y_{ij} =0)}{p(y_{ij} =1)}\right) + log \frac{1-\beta}{\beta}  }_{w_{ij}}
\end{align}
Where $\beta$ is used as a prior.

For 2D images, we took the models from \cite{andres_2011_iccv}
which are defined on the images of the Berkeley Segmentation
Database \cite{martin_2001}.
For 3D volume segmentation we took the models from
Andres \etal \cite{kroeger_2012_eccv}.
We use models with the cube sizes $150^3$, $300^3$, $450^3$, $550^3$ and $900^3$.
Both, the 2D and 3D models are available in a recent graphical model
benchmark of Kappes \etal ~\cite{kappes_2013_benchmark_cvpr}.
We use the same names for the datasets as in the benchmark,
\emph{image-seg} for the models from  \cite{andres_2011_iccv} and \emph{knott-150 - knott-550} and \emph{3d-seg}
for the models from \cite{kroeger_2012_eccv}.
The size of instances is given in tab. ~\ref{tab:instance_sizes}.

\begin{table}[H]
   \tiny
   \centering
   \caption{Datasets used for evaluation}
   \label{tab:instance_sizes}
   \begin{tabular}{llllc}
      \toprule
         Dataset          &     \#Nodes     & \#Edges  & \#Instances  & Planar        \\ 
      \midrule 
         image-seg        &     156-3764        & ???        & 100          & $\bullet$    \\ 
         knott-150        &     572-972         & ???        & 2            & $\times$ \\
         knott-300        &     3846 - 5896     & ???        & 2            & $\times$ \\
         knott-450        &     15150-17070     & ???        & 2            & $\times$ \\
         knott-550        &     27286 - 31249   & ???        & 2            & $\times$ \\
         3d-seg           &     7958 - 101220   & ???        & 2            & $\times$ \\
         slashdot         &     ???             & ???        & ???          & $\times$ \\     
      \bottomrule
   \end{tabular}
\end{table}

%\begin{center}
%    \begin{figure}
%        \begin{center}
%            \begin{subfigure}[b]{0.45\linewidth}
%                \includegraphics[width=1.0\linewidth]{images/-010.jpg}
%            \end{subfigure}
%            \quad
%            \begin{subfigure}[b]{0.45\linewidth}
%                \includegraphics[width=1.0\linewidth]{images/-030.jpg}
%            \end{subfigure}
%        \end{center}
%    \caption{
%        Raw FIBSEM data and correlation clustering result of the model from \cite{kroeger_2012_eccv%}
%    }
%    \end{figure}
%\end{center}
%
%\newpage

@@

We have presented a fast and scalable 
approximate solver for correlation 
clustering, named Fusion Moves for correlation clustering (FM-CC).
The best solution is iteratively improved 
by a fusion with proposal solutions.
The itself is formulated as correlation
clustering on a smaller graph fewer edges and nodes
and can therefore be solved very fast.
Our evaluation shows that CC-FF
significantly outperforms 
other solvers w.r.t. any time performance 
with increasing problem size.

{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\onecolumn
\section{Appendix}
